Security Metrics for the Android Ecosystem

### 2015-07-27 avostats.tex
Updated stats and figures
./update.sh
Tweak some tables and hyphenation rules to make things fit better inside the columns

\newcommand{\avoNumSubmitters}{7}
\newcommand{\avoTotalExternalLines}{25 Million}
\newcommand{\avoNumExternalProjects}{176}
\newcommand{\avoNumBigExternalLinesOfCode}{25 Million}
\newcommand{\avoBigExternalLinesOfCodePerc}{99.7\%}
\newcommand{\avoNumVulnerabilities}{31}
\newcommand{\avoNumVulnAllAndroid}{15}
\newcommand{\avoNumVulnSpecific}{16}
\newcommand{\avoStartDate}{2013-08-28}
\newcommand{\avoEndDate}{2014-10-17}
\newcommand{\avoFirstDataDate}{2010-07-13}
\newcommand{\avoLastDataDate}{2014-07-29}
\newcommand{\avoVulnsPerYearNominal}{7.66}
\newcommand{\avoVulnsPerYear}{$7.66 \pm 1.38$}
\newcommand{\avoVulnsPerYearAllAndroidNominal}{3.71}
\newcommand{\avoVulnsPerYearAllAndroid}{$3.71 \pm 0.957$}
\newcommand{\avoTabAndVulns}{\begin{table} \centering \small \begin{tabular}{l|l|c} Vulnerability & How known & Date \\ \hline KillingInTheNameOf & Fixed on & 2010-07-13 \\ exploid udev & Discovered on & 2010-07-15 \\ levitator & Discovered on & 2011-03-10 \\ Gingerbreak & Fixed on & 2011-04-18 \\ zergRush & Discovered on & 2011-10-06 \\ APK duplicate file & Discovered on & 2013-02-18 \\ APK unchecked name & Discovered on & 2013-06-30 \\ APK unsigned shorts & Fixed on & 2013-07-03 \\ vold asec & Fixed on & 2014-01-27 \\ Fake ID & Fixed on & 2014-04-17 \\ TowelRoot & Discovered on & 2014-05-03 \\\end{tabular} \caption{Critical vulnerabilities in Android} \label{tab:andvulns} \end{table}}
\newcommand{\avoNumBigExternalProjects}{40}
\newcommand{\avoNumAnalysedExternalProjects}{28}
\newcommand{\avoNumAnalysedExternalLinesOfCode}{6 Million}
\newcommand{\avoAnalysedExternalLinesOfCodePerc}{24.9\%}
\newcommand{\avoBigExternalMedianVersions}{1.5}
\newcommand{\avoBigExternalMeanVersionsNominal}{2.07}
\newcommand{\avoBigExternalMeanVersions}{$2.07 \pm 1.44$}
\newcommand{\avoBigExternalTotalVersions}{58}

>>>>

\newcommand{\avoNumSubmitters}{7}
\newcommand{\avoTotalExternalLines}{25 Million}
\newcommand{\avoNumExternalProjects}{176}
\newcommand{\avoNumBigExternalLinesOfCode}{25 Million}
\newcommand{\avoBigExternalLinesOfCodePerc}{99.7\%}
\newcommand{\avoNumVulnerabilities}{32}
\newcommand{\avoNumVulnAllAndroid}{15}
\newcommand{\avoNumVulnSpecific}{17}
\newcommand{\avoStartDate}{2013-08-28}
\newcommand{\avoEndDate}{2015-03-24}
\newcommand{\avoFirstDataDateMonth}{July 2010}
\newcommand{\avoFirstDataDate}{2010-07-13}
\newcommand{\avoLastDataDateMonth}{March 2015}
\newcommand{\avoLastDataDate}{2015-03-12}
\newcommand{\avoVulnsPerYearNominal}{6.86}
\newcommand{\avoVulnsPerYear}{$6.86 \pm 1.21$}
\newcommand{\avoVulnsPerYearAllAndroidNominal}{3.21}
\newcommand{\avoVulnsPerYearAllAndroid}{$3.21 \pm 0.83$}
\newcommand{\avoVulnsPerYearTwosfNominal}{6.9}
\newcommand{\avoVulnsPerYearTwosf}{$6.9 \pm 1.2$}
\newcommand{\avoVulnsPerYearAllAndroidTwosfNominal}{3.2}
\newcommand{\avoVulnsPerYearAllAndroidTwosf}{$3.2 \pm 0.0$}
\newcommand{\avoTabAndVulns}{\begin{table} \centering \small \begin{tabular}{l|l|c|c} Vulnerability & How known & Date & Categories\\ \hline KillingInTheNameOf & Fixed & 2010-07-13 & sys, kern\\ exploid udev & Discovered & 2010-07-15 & kernel\\ levitator & Discovered & 2011-03-10 & kernel\\ Gingerbreak & Fixed & 2011-04-18 & system\\ zergRush & Discovered & 2011-10-06 & system\\ APK duplicate file & Discovered & 2013-02-18 & signature\\ APK unchecked name & Discovered & 2013-06-30 & signature\\ APK unsigned shorts & Fixed & 2013-07-03 & signature\\ vold asec & Fixed & 2014-01-27 & system\\ Fake ID & Fixed & 2014-04-17 & signature\\ TowelRoot & Discovered & 2014-05-03 & kernel\\\end{tabular} \caption{Critical vulnerabilities in Android} \label{tab:andvulns} \end{table}}
\newcommand{\avoNumBigExternalProjects}{40}
\newcommand{\avoNumAnalysedExternalProjects}{28}
\newcommand{\avoNumAnalysedExternalLinesOfCode}{6 Million}
\newcommand{\avoAnalysedExternalLinesOfCodePerc}{24.9\%}
\newcommand{\avoBigExternalMedianVersions}{2.0}
\newcommand{\avoBigExternalMeanVersionsNominal}{2.57}
\newcommand{\avoBigExternalMeanVersions}{$2.57 \pm 1.84$}
\newcommand{\avoBigExternalTotalVersions}{72}

### 2015-07-27 dastats.tex
Tweak some tables and hyphenation rules to make things fit better inside the columns

\newcommand{\daTabDLDistances}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & summary \\ \hline equal & 0.0 & 0.0667 & 0.0 & 0.0 \\weight $m$ & 0.2 & 0.4 & 0.0714 & 0.0 \\$f$ & 0.4 & 0.667 & 0.5 & 0.0 \\weight $u$ & 0.4 & 0.0667 & 0.143 & 0.0 \\$m$ & 0.6 & 0.733 & 0.357 & 0.5 \\$u$ & 0.9 & 0.6 & 0.786 & 0.0 \\\end{tabular} \caption{Normalised Damerau-Levenshtein distances for different metrics} \label{tab:dl_distances} \end{table}}
\newcommand{\daTabChangeInScores}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & summary \\ \hline $m$ & $-1.67 \pm 2.25$ & $-0.66 \pm 2.54$ & $-3.3 \pm 1.3$ & $-3.4 \pm 1.8$ \\weight $m$ & $-0.264 \pm 0.277$ & $-0.0991 \pm 0.321$ & $-0.461 \pm 0.167$ & $-0.488 \pm 0.217$ \\equal & $-0.108 \pm 0.062$ & $-0.0367 \pm 0.112$ & $-0.146 \pm 0.045$ & $-0.165 \pm 0.033$ \\weight $u$ & $-0.0608 \pm 0.122$ & $-0.0112 \pm 0.232$ & $0.0242 \pm 0.0808$ & $-0.00596 \pm 0.12$ \\$u$ & $0.367 \pm 1.61$ & $0.219 \pm 2.12$ & $1.55 \pm 0.94$ & $1.42 \pm 1.48$ \\$f$ & $0.975 \pm 0.564$ & $0.331 \pm 1.01$ & $1.31 \pm 0.41$ & $1.48 \pm 0.3$ \\\end{tabular} \caption{Mean change in scores for different metrics} \label{tab:change_in_scores} \end{table*}}

@@

\newcommand{\daTabSpearmanRanks}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & summary \\ $\pm\sigma$ & 0.211 & 0.169 & 0.175 & 0.632 \\ \hline $u$ & 0.297 & 0.804 & 0.618 & 1.0 \\$m$ & 0.794 & 0.593 & 0.969 & -1.0 \\$f$ & 0.83 & 0.775 & 0.934 & 1.0 \\weight $u$ & 0.939 & 0.996 & 0.991 & 1.0 \\weight $m$ & 0.976 & 0.964 & 0.996 & 1.0 \\equal & 1.0 & 0.996 & 1.0 & 1.0 \\\end{tabular} \caption{Spearman Rank correlation coefficients for different metrics. The uncertainty is constant for each column but does not take into account the uncertainty in the score which produced the ranking.} \label{tab:spearman_ranks} \end{table}}

>>>>

\newcommand{\daTabDLDistances}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & nexus \\ \hline equal & 0.0 & 0.0667 & 0.0 & 0.0 \\weight $m$ & 0.2 & 0.4 & 0.0714 & 0.0 \\$f$ & 0.4 & 0.667 & 0.5 & 0.0 \\weight $u$ & 0.4 & 0.0667 & 0.143 & 0.0 \\$m$ & 0.6 & 0.733 & 0.357 & 0.5 \\$u$ & 0.9 & 0.6 & 0.786 & 0.0 \\\end{tabular} \caption{Normalised Damerau-Levenshtein distances for different metrics} \label{tab:dl_distances} \end{table}}
\newcommand{\daTabChangeInScores}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & nexus \\ \hline $m$ & $-1.67 \pm 2.25$ & $-0.66 \pm 2.54$ & $-3.3 \pm 1.3$ & $-3.4 \pm 1.8$ \\weight $m$ & $-0.264 \pm 0.277$ & $-0.0991 \pm 0.321$ & $-0.461 \pm 0.167$ & $-0.488 \pm 0.217$ \\equal & $-0.108 \pm 0.062$ & $-0.0367 \pm 0.112$ & $-0.146 \pm 0.045$ & $-0.165 \pm 0.033$ \\weight $u$ & $-0.0608 \pm 0.122$ & $-0.0112 \pm 0.232$ & $0.0242 \pm 0.0808$ & $-0.00596 \pm 0.12$ \\$u$ & $0.367 \pm 1.61$ & $0.219 \pm 2.12$ & $1.55 \pm 0.94$ & $1.42 \pm 1.48$ \\$f$ & $0.975 \pm 0.564$ & $0.331 \pm 1.01$ & $1.31 \pm 0.41$ & $1.48 \pm 0.3$ \\\end{tabular} \caption{Mean change in scores for different metrics} \label{tab:change_in_scores} \end{table*}}

@@

\newcommand{\daTabSpearmanRanks}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & nexus \\ $\pm\sigma$ & 0.211 & 0.169 & 0.175 & 0.632 \\ \hline $u$ & 0.297 & 0.804 & 0.618 & 1.0 \\$m$ & 0.794 & 0.593 & 0.969 & -1.0 \\$f$ & 0.83 & 0.775 & 0.934 & 1.0 \\weight $u$ & 0.939 & 0.996 & 0.991 & 1.0 \\weight $m$ & 0.976 & 0.964 & 0.996 & 1.0 \\equal & 1.0 & 0.996 & 1.0 & 1.0 \\\end{tabular} \caption{Spearman Rank correlation coefficients for different metrics. The uncertainty is constant for each column but does not take into account the uncertainty in the score which produced the ranking.} \label{tab:spearman_ranks} \end{table}}
